PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2020-04-01 main.tex
Collision timescale scaling with no gravitational focusing
Add discussion of gravitational focusing suppression

\begin{figure}
    \includegraphics[width=0.5\columnwidth]{figures/test.png}
    \caption{Caption goes here.\label{fig:test}}
\end{figure}

@@

>>>>

@@

Figure \ref{fig:time_eq_gf} shows the Hill eccentricity required for these two timescales to be equal as a function of orbital period (solid lines). Regions above the curves represent parameter combinations in which the relaxation timescale is longer. This is assuming that the planetesimals have an internal bulk density of 2 g cm$^{-3}$ and their collision cross section is enhanced by a factor of $f_{pl}$ to make the computation faster.

\begin{figure}
    \begin{center}
    \includegraphics[width=0.5\columnwidth]{figures/time_eq_gf.png}
    \caption{Caption goes here.\label{fig:time_eq_gf}}
    \end{center}
\end{figure}

\subsection{Inhibition of Gravitational Focusing}

The scaling relations derived above assume that the collision cross section scales as $v^{-2}$ or linearly with $r$. This is only true when the planetesimal encounter velocity is small compared to the mutual escape velocity of two planetesimals. Close to the star, this condition is violated because the encounter velocity grows with the Keplerian velocity. The minimum orbital distance at which gravitational focusing is effective can be derived by equating the encounter velocity with the mutual escape velocity

\begin{equation}
    r_{gf} \geq \frac{3 M_{*} \left< e^{2} \right> s}{4 m}
\end{equation}

Another way to think of this effect is that the gravitational capture radius of a planetesimal decreases with encounter velocity. $r_{gf}$ is the orbital distance at which the capture radius is smaller than the geometric cross section of a planetesimal.  In this case, the collision timescale instead scales as

\begin{equation}
    t_{coll} \sim A^{-1} r^{\alpha + 3/2}
\end{equation}

\noindent and the number of timesteps required to resolve a collision stays constant with $r$ for a flat ($\alpha = 0$) surface density profile.

Figure \ref{fig:time_eq_gf} also shows the minimum Hill eccentricity required to suppress gravitational focusing at a given orbital period for different values of $f_{pl}$ (dashed lines). Comparing with the solid curves, it is nearly always the case that a disk sufficiently hot enough to cause the relaxation time to exceed the collision timescale will also suppress gravitational focusing.
